On Misuses of the Kolmogorov--Smirnov Test for One-Sample Goodness-of-Fit

### 2023-04-20 manuscript/manuscript.tex
fixed AR(1) confusion in Section 4

The rest of the paper is organized as follows. Section~\ref{sec:fitted}
investigates the scenario where the hypothesized distribution has unspecified
parameters. Both parametric and nonparametric bootstrap are available to fix the
issue. Section~\ref{sec:dependence} investigates the scenario where the data of
the empirical distribution are serially dependent. A bootstrap procedure
employing a working ARMA model to account for dependence is proposed as a
working solution. Section~\ref{sec:fittedwithdependence}
explores the case where a combination of the first two scenarios occurs.
Section~\ref{sec:conclusion} concludes with a discussion.

@@

Similar to Section~\ref{sec:dependence}, the copula approach is not a complete
solution. Regardless of the true dependence in the data we assume an AR(1)
dependence structure by taking the lag-1 sample auto-spearman rho. However, we
can show that as long as the AR(1) assumption is a close approximation, the
correction still provides a reasonable approximation that can be useful for
practical purposes. Figure~\ref{fig:pp_ssf} shows the results of the
procedure performed on data generated with dependence structures of ARMA(1, 1),
AR(2), and MA(1). Naively fitting parameters and not adjusting for dependence  clearly deviates from a uniform distribution of p-values. 
Parametric bootstrap provides some correction but does not account for 
dependence, 
\eds{just want to verify: you are using parametric bootstrap from Section 2 for
the top portion of Figure~\ref{fig:pp_ssf}? (Not the totally naive procedure 
that ignores both issues)} 
so therefore the results of the copula remedy are more accurate and favorable.
In the case of MA(1) and ARMA(1, 1), the true dependence appears close enough
to our assumption of AR(1) that the results are reasonable. AR(2) however
appears to be just far enough from our assumption, showing a limitation of the
procedure. \eds{I don't think AR(2) looks that bad?}

@@

The KS test has base assumptions that the hypothesized distribution is
completely specified and the data is independent. When these assumptions are
violated, the test is no longer accurate and remedies must be performed. In the
case of fitted parameters, parametric and non-parametric bootstrap can restore
the size of the test. A bias correction is required if the non-parametric form
is used \citep{babu2004goodness}. In the case of serially dependent data, 
a procedure using bootstrap with copulas to model dependency shows positive
results. When both assumptions are violated, i.e., where the data has serial 
dependence and parameters must be fitted, an adjusted copula procedure also 
shows positive results. The tests appear effective for a variety of families of 
distributions. The copula remedy is not a complete solution and has limitations. 
Regardless of the true dependence, we assume an ARMA(p,q) dependence structure 
in the procedure in Section~\ref{sec:dependence} and an AR(1) dependence 
structure in the procedure in Section~\ref{sec:fittedwithdependence}. 
%Therefore, if the AR(1) dependence structure is a 
%close approximation of the truth, the approach can work.
%However, in cases such as AR(2) \eds{I still do not think AR(2) looks bad!}, if 
%the approximation is too far from the true
%dependence structure the approach does not completely remedy the issue.
Therefore, if the assumed dependence structure is a close approximation of the
truth, the approach can work. However, if the approximation is too far from the 
true dependence structure the approach does not completely remedy the issue. 
As well, tests were only performed with the normal copula. It is possible that 
other copulas could provide stronger results based on the true dependence of the 
data.

>>>>

The rest of the paper is organized as follows. Section~\ref{sec:fitted}
investigates the scenario where the hypothesized distribution has unspecified
parameters. Both parametric and nonparametric bootstrap are available to fix the
issue. Section~\ref{sec:dependence} investigates the scenario where the data of
the empirical distribution are serially dependent. A bootstrap procedure
employing a working ARMA model to account for dependence is proposed as a
working solution. Section~\ref{sec:fittedwithdependence}
explores the case where a combination of the first two scenarios occurs. An  
adjusted bootstrap procedure is proposed as a working solution in this case.  
Section~\ref{sec:conclusion} concludes with a discussion.

@@

Figure~\ref{fig:pp_ssf} shows the results of the
procedure performed on data generated with dependence structures of ARMA(1, 1),
AR(2), and MA(1). Naively fitting parameters and not adjusting for dependence  clearly deviates from a uniform distribution of p-values. 
Parametric bootstrap provides some correction but does not account for 
dependence, 
\eds{just want to verify: you are using parametric bootstrap from Section 2 for
the top portion of Figure~\ref{fig:pp_ssf}? (Not the totally naive procedure 
that ignores both issues)} 
so therefore the results of the copula remedy are more accurate and favorable.
%In the case of MA(1) and ARMA(1, 1), the true dependence appears close enough
%to our assumption of AR(1) that the results are reasonable. AR(2) however
%appears to be just far enough from our assumption, showing a limitation of the
%procedure.

Similar to Section~\ref{sec:dependence}, the copula approach is not a complete
solution. Regardless of the true dependence in the data we assume an ARMA$(p,q)$
dependence structure. As long as this assumption is a close approximation, the
correction should still provide a reasonable approximation that can be useful 
for practical purposes. 
%Regardless of the true dependence in the data we assume an AR(1)
%dependence structure by taking the lag-1 sample auto-spearman rho. However, we
%can show that as long as the AR(1) assumption is a close approximation, the
%correction still provides a reasonable approximation that can be useful for
%practical purposes.

@@

The KS test has base assumptions that the hypothesized distribution is
completely specified and the data is independent. When these assumptions are
violated, the test is no longer accurate and remedies must be performed. In the
case of fitted parameters, parametric and non-parametric bootstrap can restore
the size of the test. A bias correction is required if the non-parametric form
is used \citep{babu2004goodness}. In the case of serially dependent data, 
a procedure using bootstrap with copulas to model dependency shows positive
results. When both assumptions are violated, i.e., where the data has serial 
dependence and parameters must be fitted, an adjusted copula procedure also 
shows positive results. The tests appear effective for a variety of families of 
distributions. The copula remedy is not a complete solution and has limitations. 
Regardless of the true dependence, we assume an ARMA($p,q$) dependence structure. 
%Therefore, if the AR(1) dependence structure is a 
%close approximation of the truth, the approach can work.
%However, in cases such as AR(2), if 
%the approximation is too far from the true
%dependence structure the approach does not completely remedy the issue.
Therefore, if the assumed dependence structure is a close approximation of the
truth, the approach can work. However, if the approximation is too far from the 
true dependence structure the approach does not completely remedy the issue. 
As well, tests were only performed with the normal copula. It is possible that 
other copulas could provide stronger results based on the true dependence of the 
data.
